\ttitle

### 2013-10-24 Chapters/Chapter3/one_class_svm.tex
More on OCC
Adding notes from Learning from Data

The separating hyperplane is represented by
\begin{equation}
w^T x + b = 0,
\end{equation}
with $w \in F$ and $b \in R$.
The hyperplane that is created determines the \emph{margin} between the classes; the minimal distance from one of the data points to the hyperplane.
In geometric sense, $w$ is the normal vector to the hyperplane and $\frac{b}{\lVert{w}\rVert}$ determines the offset of the hyperplane to the origin.
Since the distance between the two margins is equal to $\frac{2}{\lVert{w}\rVert}$, the maximum-margin hyperplane is found by minimizing $\lVert{w}\rVert$.
The data points which lie on the margin are the \emph{support vectors}.
This geometrical interpretation is illustrated in Figure \ref{fig:svm_hyperplane}.
All data points for which $y_i = -1$ are on one side of the hyperplane and all other data points (for which $y_i = 1$) are on the other side.
The minimal distance from a data point to the hyperplane is for both classes equal.
This results in a \emph{maximal margin} between the two classes.
Thus, the \gls{svm} searches for a maximal separating hyperplane.

@@

*** TODO: better format of above formula ***

This minimization problem can be solved (using \gls{qp}) and transformed to its Lagrange dual formulation.
To do so, the Lagrange multipliers $a_i >= 0$ are introduced and the decision function becomes:
\begin{equation}\label{eq:svm_lagrange}
  f(x) = \operatorname{sgn}( \sum_{i=1}^n \alpha_i y_i K(x, x_i) + b),
\end{equation}
where $K(x, x_i) = \phi(x)^T\phi(x_i)$ (which is further discussed in section \ref{subsec:kernel_trick}).
Here every data point $\mathcal{I}$ for which $a_i > 0$ is weighted in the decision function and thus ``supports'' the classification machine: hence the name ``\acrlong{svm}''.
Since it is shown that under certain circumstances \glspl{svm} show an equality to sparse representations \cite{girosi1998equivalence,smola1998connection}, there will often be relatively few Lagrange multipliers with a non-zero value.

@@

@@

\subsection{More literature}
*** These papers need to be referenced and included ***

@@

>>>>

The separating hyperplane is represented by
\begin{equation}
w^T x + b = 0,
\end{equation}
with $w \in F$ and $b \in R$.
The hyperplane that is created determines the \emph{margin} between the classes; the minimal distance from one of the data points to the hyperplane.
In geometric sense, $w$ is the normal vector indication the direction of the hyperplane and $\frac{b}{\lVert{w}\rVert}$ determines the offset of the hyperplane to the origin.
Since the distance between the two margins is equal to $\frac{2}{\lVert{w}\rVert}$, the maximum-margin hyperplane is found by minimizing $\lVert{w}\rVert$.
The data points which lie on the margin are the \emph{support vectors}.
This geometrical interpretation is illustrated in Figure \ref{fig:svm_hyperplane}.
All data points for which $y_i = -1$ are on one side of the hyperplane and all other data points (for which $y_i = 1$) are on the other side.
The minimal distance from a data point to the hyperplane is for both classes equal.
This results in a \emph{maximal margin} between the two classes.
Thus, the \gls{svm} searches for a maximal separating hyperplane.

@@

*** TODO: better format of above formulas. Check with notation and formulas of chapter 9 of \cite{cherkassky2007learning}. ***

This minimization problem can be solved (using \gls{qp}) and transformed to its Lagrange dual formulation.
\\ *** TODO: Add explanation why to use dual, which is: because the problem formulation scales with the number of samples $n$ and not the dimesionality $d$ of the samples.
More in Section 9.3 of \cite{cherkassky2007learning}. *** \\
To do so, the Lagrange multipliers $a_i >= 0$ are introduced and the decision function becomes:
\begin{equation}\label{eq:svm_lagrange}
  f(x) = \operatorname{sgn}( \sum_{i=1}^n \alpha_i y_i K(x, x_i) + b),
\end{equation}
where $K(x, x_i) = \phi(x)^T\phi(x_i)$ (which is further discussed in section \ref{subsec:kernel_trick}).
Here every data point $\mathcal{I}$ for which $a_i > 0$ is weighted in the decision function and thus ``supports'' the classification machine: hence the name ``\acrlong{svm}''.
Since it is shown that under certain circumstances \glspl{svm} show an equality to sparse representations \cite{girosi1998equivalence,smola1998connection}, there will often be relatively few Lagrange multipliers with a non-zero value.

*** TODO: Add more on sparsity and good results, because of sparse representations, even in case of data of high dimensionality. e.g. \cite{cherkassky2007learning}. ***

@@

*** Add something about robustness, discusses in section 9.2 from \cite{cherkassky2007learning} ***

@@

-- Literature --

*** These papers need to be referenced and included ***

@@

``On simple one-class classification methods'' \cite{noumir2012simple}. 2012  --> decouples radius and center optimization, gives fast approximations instead of precise results. \\

``Learning from Data'' \cite{cherkassky2007learning}. 2007, 1547 (book).
